### 2016-03-17 thesis/ellicular.tex
corrections to chapters

\chapter{Monster black holes in compact massive spheroids with intermediate scale discs}
\label{ch:ellic}

This Chapter brings together three ``hot topics'' of today's astrophysical debate, 
that is, over-massive black holes in the $M_{\rm BH} - L_{\rm sph}$ diagram, 
the variety of bulge-to-disc ratios in local early-type galaxies, 
and the evolution of the mass-size relationship from $z=2$ to $z=0$. 
While an overview about the first two topics was given in Sections \ref{sec:monsters} and \ref{sec:photokin}, 
no mention of the mass-size relation was made in Chapter \ref{ch:intro} 
because not immediately related to SMBHs. 
Therefore, a more extensive introduction of this last point is given here. \\

It has been claimed that high-redshift passive galaxies were significanly more compact 
than their local counterparts. 
\citet{daddi2005} reported on the observation of seven quiescent early-type galaxies 
at $z=1.4-2.5$ with stellar masses $\gtrsim 10^{11} \rm~M_\odot$ 
and effective radii significantly smaller than those of local couterparts. 
\citet{trujillo2006} analysed ten massive $\approx 5 \times 10^{11} \rm~M_\odot$ galaxies at $z=1.2-1.7$ 
and measured for them sizes a factor of 4 smaller than $z=0$ galaxies with similar stellar masses. 
From this, they concluded that the observed rapid evolution of the structural properties of massive quiescent galaxies 
over the last $\approx 10 \rm~Gyr$ 
cannot be reconciled with a monolithic formation scenario. 
\citet{kriek2008} and \citet{vandokkum2008} found that nearly half of $z \approx 2$ 
massive ($\approx 10^{11} \rm~M_\odot$) galaxies 
have old stellar populations, negligible star formation, and sizes a factor of 5 smaller than 
those of local descendants, 
and silimilar conclusions were reached by several other studies 
(e.g.\citealt{toft2007,trujillo2007,zirm2007,buitrago2008,damjanov2009}). 
While some studies have pointed out that ``progenitor bias''\footnote{``Progenitor bias'' refers to sample confusion 
of the local descendants of high-redhift massive quiescent galaxies. 
While some of the $z=0$ red-sequence galaxies might have had a passive evolution since $z \approx 2$, 
other $z=0$ red-sequence galaxies might descend from $z \approx 2$ star-forming galaxies. } 
(e.g.~\citealt{carollo2014}) might play an important role 
when tracking the evolution of massive quiescent galaxies, 
minor dry mergers have been commonly advocated to explain the size growth of these galaxies 
(e.g.~\citealt{hopkins2009,carrasco2010,cimatti2012,fan2013,de2014}).
However, not enough satellites have been found around massive galaxies 
to support the minor dry mergers scenario 
(e.g.~\citealt{khochfarburkert2006,maller2006,hopkins2009,naab2009,mclure2013}). 
A fascinating solution to the problem was proposed by \citet{graham2013review}, 
who suggested that the high-redshift compact massive spheroids have evolved into the bulges 
of today's massive early-type disc galaxies (see also \citealt{dullograham2013cores} and \citealt{driver2013}). 
This view was confirmed by \citet{gds2015}, 
who used bulge/disc decomposition 
to unveil a large number of previously unnoticed local stellar spheroidal systems 
with the same structural properties, old stellar populations, 
and similar number density as the high-redshift compact massive spheroids. 
\citet{gds2015} advocated the growth of two-dimensional stellar disks around the compact massive spheroids 
to explain the evolution of these objects. \\

The remainder of this chapter comprises the published version of the paper 
``Explaining the reportedly overmassive black holes in early-type galaxies with intermediate-scale discs'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 457 of \emph{Monthly Notices of the Royal Astronomical Society}.

>>>>

\chapter{Monster Black Holes in (Compact) Massive Spheroids with Intermediate-Scale Discs}
\label{ch:ellic}

This Chapter brings together three ``hot topics'' of today's astrophysical debate, 
that is, over-massive black holes in the $M_{\rm BH} - L_{\rm sph}$ diagram, 
the variety of bulge-to-disc ratios in local early-type galaxies, 
and the evolution of the mass-size relationship from $z=2$ to $z=0$. 
While an overview about the first two topics was given in Sections \ref{sec:monsters} and \ref{sec:photokin}, 
no mention of the mass-size relation was made in Chapter \ref{ch:intro} 
because it is not immediately related to SMBHs. 
Therefore, a more extensive introduction of this last point is given here. \\

It has been claimed that a considerable number of high-redshift passive galaxies are significantly more compact 
than their local counterparts. 
\citet{daddi2005} reported on the observation of seven quiescent early-type galaxies 
at $z=1.4-2.5$ with stellar masses $\gtrsim 10^{11} \rm~M_\odot$ 
and effective radii significantly smaller than those of local counterparts. 
\citet{trujillo2006} analysed ten massive $\approx 5 \times 10^{11} \rm~M_\odot$ galaxies at $z=1.2-1.7$ 
and measured for them sizes a factor of 4 smaller than $z=0$ galaxies with similar stellar masses. 
From this, they concluded that the observed rapid evolution of the structural properties of massive quiescent galaxies 
over the last $\approx 10 \rm~Gyr$ 
cannot be reconciled with a monolithic formation scenario. 
\citet{kriek2008} and \citet{vandokkum2008} found that nearly half of $z \approx 2$ 
massive ($\approx 10^{11} \rm~M_\odot$) galaxies 
have old stellar populations, negligible star formation, and sizes a factor of 5 smaller than 
those of local descendants, 
and similar conclusions were reached by several other studies 
(e.g.\citealt{toft2007,trujillo2007,zirm2007,buitrago2008,damjanov2009}). 
While some studies have pointed out that ``progenitor bias''\footnote{``Progenitor bias'' refers to sample confusion 
of the local descendants of high-redshift massive quiescent galaxies. 
While some of the $z=0$ red-sequence galaxies might have had a passive evolution since $z \approx 2$, 
other $z=0$ red-sequence galaxies might descend from $z \approx 2$ star-forming galaxies. } 
(e.g.~\citealt{carollo2014}) might play an important role 
when tracking the evolution of massive quiescent galaxies, 
minor dry mergers have been commonly advocated to explain the size growth of these galaxies 
(e.g.~\citealt{hopkins2009,carrasco2010,cimatti2012,fan2013,de2014}).
However, not enough satellites have been found around massive galaxies 
to support the minor dry merger scenario 
(e.g.~\citealt{khochfarburkert2006,maller2006,hopkins2009,naab2009,mclure2013}). 
A fascinating solution to the problem was proposed by \citet{graham2013review}, 
who suggested that the high-redshift compact massive spheroids 
(also dubbed ``red nuggets'', \citealt{damjanov2009}) have evolved into the bulges 
of today's massive early-type disc galaxies (see also \citealt{dullograham2013cores} and \citealt{driver2013}). 
This view was confirmed by \citet{gds2015}, 
who used published, reliable bulge/disc decompositions 
to unveil a large number of previously unnoticed local stellar spheroidal systems 
with the same structural properties, old stellar populations, 
and similar number density as the high-redshift compact massive spheroids. 
\citet{gds2015} advocated the growth of two-dimensional stellar discs around the compact massive spheroids 
to explain the evolution of these objects. \\

Here we focus on five local early-type galaxies (Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115) 
for which we performed accurate multicomponent decomposition 
with the aid of photometric and kinematic information. 
Our analysis shows that these galaxies all share the same morphological structure: 
a stellar spheroidal component with the same properties (massive, compact, and old) as the high-redshift red nuggets 
and an intermediate-scale stellar disc that remains embedded within the spheroid. 
These five galaxies had their black hole masses estimated with a direct method.  
Four of them had been previously modelled by other studies \citep{rusli2011,vandenbosch2012,walsh2015,yildirim2015}, 
which failed to account for the correct radial extent of the stellar disc 
and consequently underestimated the spheroid luminosity.
This yielded unusually large $M_{\rm BH} / L_{\rm sph}$ ratios.  \\

The remainder of this Chapter comprises the published version of the paper 
``Explaining the reportedly overmassive black holes in early-type galaxies with intermediate-scale discs'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 457 of \emph{Monthly Notices of the Royal Astronomical Society}.

### 2016-03-17 thesis/galaxyvivisection.tex
corrections to chapters

The preliminary investigation presented in Chapter \ref{ch:recov-mn} \citep{savorgnan2013} 
demonstrated the need for a new, systematic and homogeneous study 
aimed at obtaining more accurate galaxy decompositions 
and refining our knowledge about black hole mass scaling relations. 
In 2013, I visited A.~Marconi, E.~Sani, and L.~K.~Hunt (co-authors of the paper \citealt{sani2011}) 
in Arcetri (Florence) for a short collaboration, 
during which I was shown their 2D galaxy decomposition method using {\tt GALFIT3} \citep{peng2010}. 
This helped set the basis for the development of my own galaxy decomposition strategy. \\

@@

The remainder of this chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. I. Disassembling Galaxies'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 222 of the \emph{The Astrophysical Journal Supplement Series}.

>>>>

The preliminary investigation presented in Chapter \ref{ch:recov-mn} \citep{savorgnan2013} 
demonstrated the need for a new, systematic and homogeneous study 
aimed at obtaining more accurate galaxy decompositions 
and refining our knowledge about black hole mass scaling relations. 
In 2013, I visited A.~Marconi, E.~Sani, and L.~K.~Hunt (co-authors of the paper \citealt{sani2011}) 
in Arcetri (Florence) for a short collaboration, 
during which I was shown their 2D galaxy decomposition method using {\tt GALFIT3} \citep{peng2010}. 
This helped set the basis for the development of my own galaxy decomposition strategy, 
which is detailed in this Chapter. \\

@@

The remainder of this Chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. I. Disassembling Galaxies'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 222 of the \emph{The Astrophysical Journal Supplement Series}.

### 2016-03-17 thesis/introduction.tex
corrections to chapters

\section{Supermassive black holes} 
An astrophysical black hole is a region of the space-time whose escape velocity is greater than the speed of light.
Black holes are the simplest objects in the Universe. 
They are completely characterised by three properties: mass, spin (or angular momentum) and electric charge. \\

@@

\subsection{Measuring black hole masses}
Techniques to measure the mass of SMBHs can be divided into two main categories: direct and indirect methods 
(see \citealt{ferrareseford2005} for a thorough review). 
In direct methods, the mass of a black hole is determined from its gravitational imprint 
in the motion of the surrounding stars or gas. 
The spatial resolution of the observing instrument has to be smaller than the size of the black hole sphere-of-influence, 
which implies challenging technology and time-consuming observations. 
In indirect methods, one adopts approximations to the direct methods 
or uses a parameter of the host galaxy as a proxy to infer the black hole mass 
on the basis of observed scaling relations. \\

@@

\subsection{Scaling relations}
Over the last three decades, observations have demonstrated that 
the black hole mass scales with a number of properties of its host spheroid 
(see Section \ref{sec:spheroid} for the meaning of the term ``spheroid''), 
on scales much larger than the black hole sphere-of-influence.
The black hole mass has been shown to correlate with 
the spheroid luminosity $L_{\rm sph}$ \citep{dressler1989,kormendyrichstone1995}, 
the spheroid stellar velocity dispersion $\sigma_*$ \citep{ferraresemerritt2000,gebhardt2000}, 
the spheroid central radial concentration of stars \citep{graham2001,grahamdriver2007}, 
the spheroid dynamical mass $M_{\rm dyn,sph}$ \citep{magorrian1998,marconihunt2003,haringrix2004}, 
the spheroid gravitational binding energy \citep{allerrichstone2007}, 
the spheroid kinetic energy of random motion \citep{feolimele2005,feolimancini2009},
the spheroid effective radius \citep{sani2011}, 
and the spheroid stellar mass (e.g.~\citealt{magorrian1998,sani2011,beifiori2012,scott2013}).
Other correlations with host galaxy parameters  -- as opposed to spheroid parameters -- have been proposed, such as with
the spiral arm pitch angle \citep{seigar2008,berrier2013}, 
the number of globular clusters \citep{burkerttremaine2010,snyder2011},
the dark matter halo \citep{ferrarese2002}
and the velocity dispersion of the globular clusters \citep{sadouncolin2012,pota2013}. 
Very recently, \cite{lasker2014anal} claimed that the black hole mass correlates equally well with the spheroid and 
the total galaxy luminosity. \\

@@

\subsection{Co-evolution and AGN feedback}
The tightness (or small scatter) of the observed black hole mass correlations led to the idea
that SMBHs and host galaxies have co-evolved with some sort of self-regulated growth.
AGN feedback has been proposed as the process by which this occurs
(e.g.~\citealt{silkrees1998,fabian1999,ostrikerciotti2005}; see \citealt{fabian2012} for a review). 
The AGN is believed to emit intense flux of photons and particles 
which can sweep the gas from the host spheroid 
and terminate both star formation and gas accretion onto the black hole. 
This idea is motivated by the fact that the black hole binding energy ($\propto M_{\rm BH} c^2$) 
is much larger than the bulge binding energy ($\propto M_{\rm dyn,sph} \sigma_*^2$). 
Therefore, if just a very small percentage of the AGN energy output couples to the gas, 
all of the gas reservoir can be blown away from the host galaxy. 
The current picture distinguishes between ``quasar mode AGN feedback'', 
which takes place when the AGN energy output is close to the Eddington limit\footnote{The Eddington 
limit is the maximum luminosity at which an object can emit 
owing to balance between the outward radiation pressure and the inward gravitational force. } 
and whose main effect is to blow gas away from the spheroid, 
and ``radio mode AGN feedback'', also known as ``maintenance mode'', 
which injects energy into the interstellar gas and prevents it from cooling. \\

@@

\subsection{The S\'ersic/core-S\'ersic paradigm}  
\label{sec:bent}
For many years, the samples of galaxies with a direct measurement of their black hole mass 
had been dominated by early-type, high-luminosity galaxies, hosting the most massive black holes known. 
From these samples, the $M_{\rm BH} - M_{\rm dyn,sph}$ and $M_{\rm BH} - L_{\rm sph}$ log-linear relations 
had been reported to have an exponent $\beta$ close to 1 (i.e.~$M_{\rm BH} \propto M_{\rm dyn,sph}^{\beta \simeq 1}$). 
However, \cite{graham2012bent} addressed a crucial inconsistency, 
that becomes clear when one considers the following points.

@@

\subsection{S\'ersic and core-S\'ersic spheroids} 
\label{sec:corser}
The nomenclature \emph{S\'ersic}/\emph{core-S\'ersic} was introduced as a consequence of an observed dichotomy 
in the nature of the central surface brightness profile of stellar spheroids (elliptical galaxies or the bulges of disc galaxies). 
The surface brightness profile of S\'ersic spheroids is well described by the S\'ersic (\citeyear{sersic1963}, \citeyear{sersic1968}) model 
all over its radial extent, including the innermost central parsecs. 
Occasionally, the surface brightness profile of S\'ersic spheroids can exhibit a nuclear light excess, 
due to the contribution of an additional stellar component (e.g.~a nuclear star cluster) on top of the stellar spheroid itself. 
The surface brightness profile of core-S\'ersic spheroids is characterised by the presence of a partially depleted core, 
i.e.~a central deficit of stellar light not caused by dust obscuration. 
Beyond the region affected by the partially depleted core, 
the surface brightness profile of core-S\'ersic spheroids is well approximated by the S\'ersic (\citeyear{sersic1963}, \citeyear{sersic1968}) model. 
The core-S\'ersic model \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} provides an excellent description 
of the overall surface brightness profile of core-S\'ersic spheroids. 
Core-S\'ersic spheroids fall also into the category of ``core galaxies'', as given by the Nuker definition \citep{lauer2007}, 
although $\approx 20\%$ of ``core galaxies'' are not core-S\'ersic galaxies \citep{dullograham2014cores}, 
i.e.~they do not have depleted cores.
Figure \ref{fig:corser} illustrates the dichotomy between a S\'ersic and a core-S\'ersic spheroid. 
The presence of a partially depleted core is detected in the surface brightness profile of NGC 3348, 
whereas the best-fit model for NGC 5831 is essentially a pure S\'ersic model. \\

@@

\subsection{Origin of SMBHs}
As of today, the formation of SMBHs is still an unsolved puzzle. 
The key astrophysical questions that pertain to this open debate are: 
(\emph{i}) what are the initial seeds of SMBHs and when did they form? 
(\emph{ii}) how were these seeds distributed in the early universe 
(i.e.~what is their mass distribution function and space density)? 
and (\emph{iii}) what is their accretion history throughout the Universe's first few billion years? 
\cite{volonteribellovary2012} review three possible pathways -- not mutually exclusive -- 
that have been proposed as viable mechanisms to SMBH seeds formation. \\

@@

\subsection{Monster black holes}
\label{sec:monsters}
Over the last five years, several claims of detections of \emph{over-massive} black holes accumulated in the literature. 
Over-massive black holes are black holes whose mass is significantly larger 
than what is expected from the galaxy's spheroid stellar velocity dispersion or stellar mass, 
i.e.~they are positive outliers in the $M_{\rm BH} - \sigma_*$ or $M_{\rm BH} - M_{\rm *,sph}$ diagrams. \\

@@

\section{Galaxy decomposition}
Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution
of galaxies using a combination of analytic functions (usually one function per
galaxy component, such as spheroid, disc, bar, nucleus, etc.). 
The 1D (one-dimensional) technique begins with fitting isophotes to the galaxy image.
Isophotes are curves along which the intensity of light is constant 
and they are typically described with concentric ellipses.  
The 1D surface brightness radial profile is then extracted and modelled with a combination of 1D analytic functions. 
With the 2D (two-dimensional) technique one fits 2D analytic functions directly to digital images. 
Galaxy decomposition is useful to perform structural analysis of galaxies and obtain the best-fit 
parameters of the spheroidal component, such as the luminosity, the half-light radius 
and the central radial concentration of stars. \\

@@

\subsection{Photometry and kinematics}
\label{sec:photokin}
Early-type galaxies can exhibit a wide variety of kinematic features, 
going from the fainter rotationally-supported systems to the brighter dispersion-dominated ones (e.g.~\citealt{davies1983}). 
While the identification of stellar discs in images of spiral galaxies is generally trivial thanks to the presence of spiral arms, 
featureless discs in bright, early-type galaxies can be particularly hard to recognise 
by looking at the photometry alone, due to well-known inclination effects (e.g.\citealt{rixwhite1990,gerhardbinney1996}). 
However, this problem can be alleviated with the use of kinematic information
(e.g.~\citealt{carter1987,franx1989,nieto1991,rixwhite1992,cinzanovandermarel1993,donofrio1995,graham1998fornax}).
In particular, our understanding of the internal structure of early-type galaxies has undoubtedly improved over the past decade 
thanks to the introduction of integral-field spectrographs and the analysis of two-dimensional kinematic maps 
(e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}). \\

@@

\subsection{A compendium of the previous literature }
Over the past nine years, five independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal}
have attempted galaxy decomposition 
for samples of galaxies with a direct measure of the black hole mass. 
The main aim of each study was to derive the parameters of the spheroidal components of their galaxies 
and explore correlation with the black hole mass.
Table \ref{tab:lit} summarises the main characteristics and findings of each work. 
%The last column refers to the study presented in this thesis 
%and highlights its improvements over the past literature.

@@

\section{Thesis outline}
The aim of this thesis is to refine and re-investigate several black hole mass scaling relations 
through the careful modelling of the spatial light distribution 
of a selected sample of 66 nearby galaxies. 
After obtaining robust structural parameters for the galaxies under study, 
I will explore substructure in the correlations between these parameters and the black hole mass, 
and explain discrepancies in the results presented in the past literature. \\

>>>>

\section{Supermassive Black Holes} 
An astrophysical black hole is a region of the space-time whose escape velocity is greater than the speed of light.
Black holes are the simplest objects in the Universe. 
They are completely characterised by three properties: mass, spin (or angular momentum) and electric charge. \\

@@

\subsection{Measuring Black Hole Masses}
Techniques to measure the mass of SMBHs can be divided into two main categories: direct and indirect methods 
(see \citealt{ferrareseford2005} for a thorough review). 
In direct methods, the mass of a black hole is determined from its gravitational imprint 
in the motion of the surrounding stars or gas. 
The spatial resolution of the observing instrument has to be smaller than the size of the black hole sphere-of-influence, 
which implies challenging technology and time-consuming observations. 
In indirect methods, one adopts approximations to the direct methods 
or uses a parameter of the host galaxy as a proxy to infer the black hole mass 
on the basis of observed scaling relations. \\

@@

\subsection{Scaling Relations}
Over the last three decades, observations have demonstrated that 
the black hole mass scales with a number of properties of its host spheroid 
(see Section \ref{sec:spheroid} for the meaning of the term ``spheroid''), 
on scales much larger than the black hole sphere-of-influence.
The black hole mass has been shown to correlate with 
the spheroid luminosity $L_{\rm sph}$ \citep{dressler1989,kormendyrichstone1995}, 
the spheroid stellar velocity dispersion $\sigma_*$ \citep{ferraresemerritt2000,gebhardt2000}, 
the spheroid central radial concentration of stars \citep{graham2001,grahamdriver2007}, 
the spheroid dynamical mass $M_{\rm dyn,sph}$ \citep{magorrian1998,marconihunt2003,haringrix2004}, 
the spheroid gravitational binding energy \citep{allerrichstone2007}, 
the spheroid kinetic energy of random motion \citep{feolimele2005,feolimancini2009},
the spheroid effective radius \citep{sani2011}, 
and the spheroid stellar mass (e.g.~\citealt{magorrian1998,sani2011,beifiori2012,scott2013}).
Other correlations with host galaxy parameters  -- as opposed to spheroid parameters -- have been proposed, such as with
the spiral arm pitch angle \citep{seigar2008,berrier2013}, 
the number of globular clusters \citep{burkerttremaine2010,snyder2011},
the dark matter halo \citep{ferrarese2002}
and the velocity dispersion of the globular clusters \citep{sadouncolin2012,pota2013}. 
Very recently, \cite{lasker2014anal} claimed that the black hole mass correlates equally well with the spheroid and 
the total galaxy luminosity. \\

@@

\subsection{Co-evolution and AGN Feedback}
The tightness (or small scatter) of the observed black hole mass correlations led to the idea
that SMBHs and host galaxies have co-evolved with some sort of self-regulated growth.
AGN feedback has been proposed as the process by which this occurs
(e.g.~\citealt{silkrees1998,fabian1999,ostrikerciotti2005}; see \citealt{fabian2012} for a review). 
The AGN is believed to emit intense flux of photons and particles 
which can sweep the gas from the host spheroid 
and terminate both star formation and gas accretion onto the black hole. 
This idea is motivated by the fact that the black hole binding energy ($\propto M_{\rm BH} c^2$) 
is much larger than the bulge binding energy ($\propto M_{\rm dyn,sph} \sigma_*^2$). 
Therefore, if just a very small percentage of the AGN energy output couples to the gas, 
all of the gas reservoir can be blown away from the host galaxy. 
The current picture distinguishes between ``quasar mode AGN feedback'', 
which takes place when the AGN energy output is close to the Eddington limit\footnote{The Eddington 
limit is the maximum luminosity at which an object can emit 
owing to balance between the outward radiation pressure and the inward gravitational force. } 
and whose main effect is to blow gas away from the spheroid, 
and ``radio mode AGN feedback'', also known as ``maintenance mode'', 
which injects energy into the interstellar gas and prevents it from cooling. \\

@@

\subsection{The S\'ersic/Core-S\'ersic Paradigm}  
\label{sec:bent}
For many years, the samples of galaxies with a direct measurement of their black hole mass 
had been dominated by early-type, high-luminosity galaxies, hosting the most massive black holes known. 
From these samples, the $M_{\rm BH} - M_{\rm dyn,sph}$ and $M_{\rm BH} - L_{\rm sph}$ log-linear relations 
had been reported to have an exponent $\beta$ close to 1 (i.e.~$M_{\rm BH} \propto M_{\rm dyn,sph}^{\beta \simeq 1}$). 
However, \cite{graham2012bent} addressed a crucial inconsistency, 
that becomes clear when one considers the following points.

@@

\subsection{S\'ersic and Core-S\'ersic Spheroids} 
\label{sec:corser}
The nomenclature \emph{S\'ersic}/\emph{core-S\'ersic} was introduced as a consequence of an observed dichotomy 
in the nature of the central surface brightness profile of stellar spheroids (elliptical galaxies or the bulges of disc galaxies). 
The surface brightness profile of S\'ersic spheroids is well described by the S\'ersic (\citeyear{sersic1963}, \citeyear{sersic1968}) model 
all over its radial extent, including the innermost central parsecs. 
Occasionally, the surface brightness profile of S\'ersic spheroids can exhibit a nuclear light excess, 
due to the contribution of an additional stellar component (e.g.~a nuclear star cluster) on top of the stellar spheroid itself. 
The surface brightness profile of core-S\'ersic spheroids is characterised by the presence of a partially depleted core, 
i.e.~a central deficit of stellar light not caused by dust obscuration. 
Beyond the region affected by the partially depleted core, 
the surface brightness profile of core-S\'ersic spheroids is well approximated by the S\'ersic (\citeyear{sersic1963}, \citeyear{sersic1968}) model. 
The core-S\'ersic model \citep{graham2003coresersicmodel,trujillo2004coresersicmodel} provides an excellent description 
of the overall surface brightness profile of core-S\'ersic spheroids. 
Core-S\'ersic spheroids fall also into the category of ``core galaxies'', as given by the Nuker definition \citep{lauer2007}, 
although $\approx 20\%$ of ``core galaxies'' are not core-S\'ersic galaxies \citep{dullograham2014cores}, 
i.e.~they do not have depleted cores.
Figure \ref{fig:corser} illustrates the dichotomy between a S\'ersic and a core-S\'ersic spheroid. 
The presence of a partially depleted core is detected in the surface brightness profile of NGC 3348, 
whereas the best-fit model for NGC 5831 is essentially a pure S\'ersic model. \\

@@

\subsection{Origin of Supermassive Black Holes}
As of today, the formation of SMBHs is still an unsolved puzzle. 
The key astrophysical questions that pertain to this open debate are: 
(\emph{i}) what are the initial seeds of SMBHs and when did they form? 
(\emph{ii}) how were these seeds distributed in the early universe 
(i.e.~what is their mass distribution function and space density)? 
and (\emph{iii}) what is their accretion history throughout the Universe's first few billion years? 
\cite{volonteribellovary2012} review three possible pathways -- not mutually exclusive -- 
that have been proposed as viable mechanisms to SMBH seeds formation. \\

@@

\subsection{Monster Black Holes}
\label{sec:monsters}
Over the last five years, several claims of detections of \emph{over-massive} black holes accumulated in the literature. 
Over-massive black holes are black holes whose mass is significantly larger 
than what is expected from the galaxy's spheroid stellar velocity dispersion or stellar mass, 
i.e.~they are positive outliers in the $M_{\rm BH} - \sigma_*$ or $M_{\rm BH} - M_{\rm *,sph}$ diagrams. \\

@@

\section{Galaxy Decomposition}
Galaxy decomposition is a parametric analysis that allows one to fit the surface brightness distribution
of galaxies using a combination of analytic functions (usually one function per
galaxy component, such as spheroid, disc, bar, nucleus, etc.). 
The 1D (one-dimensional) technique begins with fitting isophotes to the galaxy image.
Isophotes are curves along which the intensity of light is constant 
and they are typically described with concentric ellipses.  
The 1D surface brightness radial profile is then extracted and modelled with a combination of 1D analytic functions. 
With the 2D (two-dimensional) technique one fits 2D analytic functions directly to digital images. 
Galaxy decomposition is useful to perform structural analysis of galaxies and obtain the best-fit 
parameters of the spheroidal component, such as the luminosity, the half-light radius 
and the central radial concentration of stars. \\

@@

\subsection{Photometry and Kinematics}
\label{sec:photokin}
Early-type galaxies can exhibit a wide variety of kinematic features, 
going from the fainter rotationally-supported systems to the brighter dispersion-dominated ones (e.g.~\citealt{davies1983}). 
While the identification of stellar discs in images of spiral galaxies is generally trivial thanks to the presence of spiral arms, 
featureless discs in bright, early-type galaxies can be particularly hard to recognise 
by looking at the photometry alone, due to well-known inclination effects (e.g.\citealt{rixwhite1990,gerhardbinney1996}). 
However, this problem can be alleviated with the use of kinematic information
(e.g.~\citealt{carter1987,franx1989,nieto1991,rixwhite1992,cinzanovandermarel1993,donofrio1995,graham1998fornax}).
In particular, our understanding of the internal structure of early-type galaxies has undoubtedly improved over the past decade 
thanks to the introduction of integral-field spectrographs and the analysis of two-dimensional kinematic maps 
(e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}). \\

@@

\subsection{A Compendium of the Previous Literature }
Over the past nine years, five independent studies 
\citep{grahamdriver2007,sani2011,vika2012,beifiori2012,lasker2014data,lasker2014anal}
have attempted galaxy decomposition 
for samples of galaxies with a direct measure of the black hole mass. 
The main aim of each study was to derive the parameters of the spheroidal components of their galaxies 
and explore correlation with the black hole mass.
Table \ref{tab:lit} summarises the main characteristics and findings of each work. 
%The last column refers to the study presented in this thesis 
%and highlights its improvements over the past literature.

@@

\section{Thesis Outline}
The aim of this thesis is to refine and re-investigate several black hole mass scaling relations 
through the careful modelling of the spatial light distribution 
of a selected sample of 66 nearby galaxies. 
After obtaining robust structural parameters for the galaxies under study, 
I will explore substructure in the correlations between these parameters and the black hole mass, 
and explain discrepancies in the results presented in the past literature. \\

### 2016-03-17 thesis/mm.tex
conclusions ellicular
corrections to chapters

In Chapter \ref{ch:galviv}, reliable and accurate multicomponent decompositions were presented 
for 66 galaxies out of the 75 belonging to the initial sample. 
These 66 galaxies constitute our final sample, 
which is currently the largest sample to date used to investigate correlations between 
directly measured black hole masses and host galaxy parameters. \\

@@

\item Some studies have distinguished pseudobulges and classical bulges according to their S\'ersic index, 
      and claimed that in the $M_{\rm BH} - L_{\rm sph}$ diagram 
      pseudobulges are offset from the correlation defined by classical bulges. 
      Here we test this result with our data.

@@

A robust linear regression analysis is crucial for the study of black hole mass correlations.
In particular, more emphasis is typically given to the slope rather than the intercept of scaling relations, 
because the slope is the parameter that theoretical models (currently) predict. 
Several studies (e.g.~\citealt{tremaine2002,graham2007,tundo2007,graham2016review}) 
have pointed out inconsistencies between the values of the slope
measured by different groups for the same correlation. 
These discrepancies can arise from the use of different galaxy samples, 
selection biases, or the statistical techniques used to perform the linear regression analysis. \\

@@

The remainder of this chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
II. The Red and Blue Sequence in the $M_{\rm BH} - M_{\rm *,sph}$ Diagram'' 
by G.~A.~D.~Savorgnan et al.,  
as it appears in Volume 817 of the \emph{The Astrophysical Journal}.

\includepdf[pages={1-12}]{ApJ2016.pdf}

>>>>

In Chapter \ref{ch:galviv}, reliable and accurate multicomponent decompositions were presented 
for 66 galaxies, our final sample, out of the 75 belonging to the initial sample. 
These 66 galaxies currently constitute the largest sample to date 
with reliable and homogeneous (i.e.~derived in a systematic and consistent manner) 
structural decompositions 
that can be used to investigate correlations between 
directly measured black hole masses and host galaxy parameters. \\

@@

\item Some studies have distinguished pseudo-bulges and classical bulges according to their S\'ersic index, 
      and claimed that in the $M_{\rm BH} - L_{\rm sph}$ diagram 
      pseudo-bulges are offset from the correlation defined by classical bulges. 
      Here we test this result with our data.

@@

A robust linear regression analysis is crucial for the study of black hole mass correlations.
In particular, more emphasis is typically given to the slope rather than the intercept of scaling relations, 
because the slope is the parameter that theoretical models (currently) 
predict\footnote{However, more and more attention is being paid to the intercept of black hole mass scaling relations, 
which plays a major role for the prediction of cosmic gravitational waves background from SMBH binary coalescence 
(e.g.~\citealt{shannon2015,shankar2016}), 
the derivation of the SMBH mass function and space density, 
or the calibration of the reverberation mapping virial factor. }. 
Several studies (e.g.~\citealt{tremaine2002,graham2007,tundo2007,graham2016review}) 
have pointed out inconsistencies between the values of the slope
measured by different groups for the same correlation. 
These discrepancies can arise from the use of different galaxy samples, 
selection biases, or the statistical techniques used to perform the linear regression analysis. \\

@@

The remainder of this Chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
II. The Red and Blue Sequence in the $M_{\rm BH} - M_{\rm *,sph}$ Diagram'' 
by G.~A.~D.~Savorgnan et al.,  
as it appears in Volume 817 of the \emph{The Astrophysical Journal}.

\includepdf[pages={1-12}]{ApJ2016a.pdf}

### 2016-03-17 thesis/recovery-mn.tex
corrections to chapters

\chapter{The recovery of the $M_{\rm BH} - n_{\rm sph}$ relation}
\label{ch:recov-mn}

@@

The remainder of this chapter comprises the published version of the paper 
``The supermassive black hole mass -- S\'ersic index relations for bulges and elliptical galaxies''
by G.~A.~D.~Savorgnan et al., 
as it appears in Volume 434 of \emph{Monthly Notices of the Royal Astronomical Society}.

>>>>

\chapter{The Recovery of the $M_{\rm BH} - n_{\rm sph}$ Relation}
\label{ch:recov-mn}

@@

The remainder of this Chapter comprises the published version of the paper 
``The supermassive black hole mass -- S\'ersic index relations for bulges and elliptical galaxies''
by G.~A.~D.~Savorgnan et al., 
as it appears in Volume 434 of \emph{Monthly Notices of the Royal Astronomical Society}.

### 2016-03-17 thesis/ubermassive-msigma.tex
corrections to chapters

\chapter{Monster black holes in Central Cluster Galaxies}
\label{ch:msigma}

@@

than any other early-type galaxy. 

@@

where the nomenclature is self-esplicative. \\

@@

The remainder of this chapter comprises the published version of the paper 
``Overmassive black holes in the $M_{\rm BH} - \sigma$ diagram 
do not belong to over (dry) merged galaxies'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 446 of \emph{Monthly Notices of the Royal Astronomical Society}.

>>>>

\chapter{Monster Black Holes in Massive Galaxies}
\label{ch:msigma}

@@

than any other early-type galaxy (see also \citealt{kormendyho2013}). 

@@

where the nomenclature is self-explicative. \\

@@

The remainder of this Chapter comprises the published version of the paper 
``Overmassive black holes in the $M_{\rm BH} - \sigma$ diagram 
do not belong to over (dry) merged galaxies'' 
by G.~A.~D.~Savorgnan \& A.~W.~Graham,  
as it appears in Volume 446 of \emph{Monthly Notices of the Royal Astronomical Society}.
